---
title: "Writing Reports with R Markdown"
author: "Waselus, Maria"
date: "`r Sys.Date()`"
output: html_document
---
```{r}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
library(here)
library(knitr)
```

This report was prepared for the UN.  It analyzes the relationship between a country's GDP, life expectancy, and CO2 emissions.  Our goal was to determine to what degree a country's economic strength or weakness may be related to its public health status and impact on climate pollution.  We hypothesize that both life expectancy and CO2 emissions will increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv(here("data/gapminder_1997.csv"))
spec(gapminder_1997)
```

```{r gdp_lifeexp_1997}
ggplot(gapminder_1997, aes(x = gdpPercap, y = lifeExp, color = continent,
                           size = pop/1000000)) +
geom_point() +
  labs(x = "GDP per capita",
       y = "Life expectancy",
      title = "Do people in wealthy countries live longer?",
      size = "Population (in millions)",
      color = "Continent")
```

```{r summary_data}
n_countries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()

min_gdp <- gapminder_1997 %>%
  summarise(min = round(min(gdpPercap)))

max_gdp <- gapminder_1997 %>%
  summarise(max = round(max(gdpPercap)))
```

The above plot shows the relationship between the GDP  per capita and life expectancy for a total of `r n_countries` countries.  For this set of countries, economic wealth ranged from a minimum of $`r min_gdp` to a maximum of $`r max_gdp`` per capita. 

|   Summary of Data   |
|----------|----------|
|   Number of countries | `r n_countries` |
|   Minimum GDP per cap |   `r min_gdp`   |
|   Maximum GDP per cap |   `r max_gdp`   |

```{r tables}
gapminder_1997 %>%
  filter(continent == "Oceania") %>%
  kable()
```

## lists

### Unordered lists
- **R**
   - subitem
- *ggplot*
- ***stringr*** package

### Ordered lists
1. **R**
1. *ggplot*
1. ***stringr*** package
1. [RMarkdown Reference](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)
